Considering scale in multilayer animal social networks

### 2020-06-11 paper/manuscript.Rmd
sri

where x is the number of fixes where individuals A and B were within a given
distance of each other, $y_{A}$ is the number of fixes from individual A when
individual B did not have a simultaneous fix, $y_{B}$ is the number of fixes
from individual B when individual A did not have a simultaneous fix, and
$y_{AB}$ is the number of simultaneous fixes from individuals A and B that were
separated by more than the given distance [@Farine_2015]. <!-- TODO: rm repeat?-->Social groups were
designated if two or more individuals occurred within a given distance of one
another at any given time point.

(ref:ml) Visualization of multilayer network for social ungulate case study representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland in summer 2017 and winter 2018. Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each individual is represented by a unique color. Six layers represent combinations of two seasons (summer and winter) and three habitat classes (open, forest and forage). Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI). Interlayer edges connect individuals to themselves across seasons and within habitat classes (e.g. individual "A" in summer, forest and individual "A" in winter, forest).

>>>>

where x is the number of fixes where individuals A and B were in the same group,
$y_{A}$ is the number of fixes from individual A when individual B did not have
a simultaneous fix, $y_{B}$ is the number of fixes from individual B when
individual A did not have a simultaneous fix, and $y_{AB}$ is the number of
simultaneous fixes from individuals A and B that were separated by more than the
spatial distance threshold [@Farine_2015].
